Data Pre-Processing

### 2021-05-04 AST-Framing-Ontario/Data Pre-Processesing.rmd
Stop Words Update
Updated stops words text file

Load the following packages:
```{r}
library(tm)
library(readr)
library(tools)
library(dplyr)
library(tidytext)
library(topicmodels)
library(ggplot2)
library(wordcloud)
#library(word2vec)
library(pdftools)
library(reshape2)
library(text2vec)
```

@@

Corpora will be cleaned for white spaces, punctuation, English stop words, and converted to lowercase. Any additional stop words will need to be removed manually as the user sees fit. 'corpusKey' is a data frame that indicates which file a corpus was derived from. 
```{r}
# Stop words for each of the corpora, or based on how your directory organizes files 
# Add stop words if you have more than 4 corpora 
NAwords2 <- c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "tip", "london", "provides", "elgin", "find", "make", "active", "travel", "lord", "holy", "toronto", "-")
NAwords3 <- c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get")
NAwords4 <- c("active", "and", "asst", "board", "can", "cancellations", "catholic", "contact", "cycling", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "walking", "waterloo", "website", "will")
NAwords1 <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "use", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "intrument", "may")

@@

```{r}
#eval(parse(text = paste("NAwords", 1, sep = "")))
NAwords1

>>>>

Load the following packages:
```{r}
library(tm)
library(readr)
library(tools)
library(dplyr)
library(tidytext)
library(topicmodels)
library(ggplot2)
library(wordcloud)
library(word2vec)
library(pdftools)
library(reshape2)
library(text2vec)
```

@@

Corpora will be cleaned for white spaces, punctuation, English stop words, and converted to lowercase. Any additional stop words will need to be removed manually as the user sees fit. 'corpusKey' is a data frame that indicates which file a corpus was derived from. 
```{r}
# Stop words for each of the corpora, or based on how your directory organizes files 
# Add stop words if you have more than 4 corpora

NAwords1 <- c("school", "transportation", "can", "use", "active", "et", "al", "travel", "study", "elsevier", "na", "sciencedirect", "journal", "transport", "mode", "modes", "children", "the", "n", "s", "schools", "also", "p", "b", "used", "number", "data", "research", "variable", "variables", "author", "authors", "researcher", "researchers", "project", "instrument", "may", "model", "studies", "one", "table", "results", "found", "likely", "using", "less", "high", "within", "associated", "however", "among", "two", "km", "eg", "m", "j", "c", "sample", "per", "three", "r", "ie", "across", "around", "well", "a", "example", "although", "t", "fig", "signiufbcant", "1/4", "ats", "d", "literature", "overall", "'", "f", "paper", "e", "therefore", "thus", "methods", "deparmant", "result", "collected", "-")

NAwords2 <- c("login", "css", "sir", "waterloo", "niagara", "john", "school", "transportation", "york", "ottawa", "can", "london", "provides", "elgin", "find", "make", "lord", "holy", "toronto", "get", "please", "will", "also", "copyright", "canada", "ontario", "translate", "download", "email", "one", "arthur", "de", "info", "website", "x")

NAwords3 <- c("york", "lane", "school", "transportation", "region", "halton", "can", "use", "guelph", "kingston", "durham", "get", "uf", "ontario", "contact", "also", "covid", "c", "e", "one", "eg", "-", "please", "canada", "n", "page", "canadian", "email", "o", "peel", "fort", "frances", "phone", "r", "ottawa", "barrie", "km", "next", "per", "thunder", "simcoe", "website", "wellington", "andor", "catholic", "k", "m", "middlesex", "oxford", "perth", "po", "provincial", "tollfree", "toronto", "ufc")

NAwords4 <- c("and", "asst", "board", "can", "cancellations", "catholic", "contact", "district", "east", "gta", "https", "login", "may", "or", "please", "school", "schools", "stp", "student", "students", "the", "transportation", "tri", "waterloo", "website", "will", "uf", "ontario", "-", "us", "north", "km", "county", "ottawa", "guelph", "ext", "phone", "e", "ps", "'s", "du", "toronto", "email", "o", "ottschoolbus", "simcoe", "canada", "careers", "covid", "facts", "ufd", "york", "pm", "ufa", "ufe", "wrdsb", "andor", "erin", "kg", "transporta", "cambridge", "httpsvimeocom", "muskoka", "stopr", "ufc", "windsor", "a", "durham", "geoquery", "hamiltonwentworth", "httpswwwwrdsbcaplanningwp", "hwdsb", "ic", "jk", "kawartha", "ng", "northeastern", "sudbury", "timiskaming", "wellingtondu")

@@

```{r}

paste(sort(NAwords4), collapse = " ")
